---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ASGSmaps

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

ASGSmaps is an API wrapper for the [Australian Statistical Geography Standard (ASGS) Edition 3](https://www.abs.gov.au/statistics/standards/australian-statistical-geography-standard-asgs-edition-3/jul2021-jun2026) from the [Australian Bureau of Statistics (ABS)](https://www.abs.gov.au/). It includes functions to access information about statistical geography standards and to download the data from the [ABS API](https://www.abs.gov.au/statistics/standards/australian-statistical-geography-standard-asgs-edition-3/jul2021-jun2026/access-and-downloads/data-services-and-apis).

## Installation

You can install the development version of ASGSmaps like so:

``` {r}
# # install remotes package
# install.packages('remotes')
# # install ASGSmaps from github
# remotes::install_github()

```



## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ASGSmaps)

# get a list of ASGS services available
available_services()

# get a list of standards available within a service
available_standards('ASGS2021')

# get a description of an available standard
standard_description('ASGS2021', 'STE')

# get a list of fields available within a standard
standard_fields('ASGS2021', 'STE')

# get a list of unique values from a field
field_values('ASGS2021', 'STE', 'STATE_NAME_2021')

# use the information to build a query
map <- get_map_data(
  service = 'ASGS2021',
  standard = 'STE',
  where = "STATE_NAME_2021 IN ('New South Wales')"
)

plot(map$geometry)

```

